\section{结论}
本文基于真实项目代码给出了一个可复现的“教师--学生”框架：用经典仿真生成 FALQON 轨迹作为监督信号，用神经网络零次推理预测整段参数序列，并通过重放演化得到能量与 Cut 值，从而以近似比 $\mathrm{AR}$ 量化替代反馈测量的效果。后续工作将聚焦于：在固定 $n=12,20$ 的外推数据集上进行同口径对比；将谱统计显式编码为多 token 输入以增强结构可解释性；以及在更贴近 NISQ 的噪声模型下评估“零次推理”对采样开销的真实收益。

\begin{thebibliography}{99}

\bibitem{ref1}
arXiv:2405.00781v2 [quant-ph] 8 May 2025,
\url{https://arxiv.org/pdf/2405.00781}



\bibitem{ref2}
Robust Feedback-Based Quantum Optimization: Analysis of Coherent Control Errors. IEEE Xplore,
\url{https://ieeexplore.ieee.org/iel8/11157924/11157953/11158422.pdf}

\bibitem{ref3}
Feedback-Based Quantum Optimization. ResearchGate,
\url{https://www.researchgate.net/publication/366240286_Feedback-Based_Quantum_Optimization}

\bibitem{ref4}
Adaptive Sampling Noise Mitigation Technique for Feedback-based Quantum Algorithms,
\url{https://www.iccs-meeting.org/archive/iccs2024/papers/148370309.pdf}

\bibitem{ref5}
Robust feedback-based quantum optimization: analysis of coherent control errors,
\url{https://www.researchgate.net/publication/393379559_Robust_feedback-based_quantum_optimization_analysis_of_coherent_control_errors}

\bibitem{ref6}
Extending QAOA-GPT to Higher-Order Quantum Optimization Problems. arXiv,
\url{https://arxiv.org/html/2511.07391v1}

\bibitem{ref7}
QAOA Parameter Transferability for Maximum Independent Set using Graph Attention Networks. ResearchGate,
\url{https://www.researchgate.net/publication/391329610_QAOA_Parameter_Transferability_for_Maximum_Independent_Set_using_Graph_Attention_Networks}

\bibitem{ref8}
Laplacian Canonization: A Minimalist Approach to Sign and Basis Invariant Spectral Embedding. NeurIPS,
\url{https://proceedings.neurips.cc/paper_files/paper/2023/file/257b3a7438b1f3709e91a86adf2fdc0a-Paper-Conference.pdf}

\bibitem{ref9}
Sign and Basis Invariant Networks for Spectral Graph Representation Learning. ICLR 2026,
\url{https://iclr.cc/virtual/2022/8714}

\bibitem{ref10}
Short Cycles in Random Regular Graphs. ResearchGate,
\url{https://www.researchgate.net/publication/220342833_Short_Cycles_in_Random_Regular_Graphs}

\bibitem{ref11}
Edge rigidity and universality of random regular graphs of intermediate degree,
\url{https://www.unige.ch/~knowles/rrg_edge.pdf}

\bibitem{ref12}
Transferability of optimal QAOA parameters between random graphs,
\url{https://www.computer.org/csdl/proceedings-article/qce/2021/169100a171/1yEZ9MWWjSg}

\bibitem{ref13}
Robust feedback-based quantum optimization: analysis of coherent control errors. arXiv,
\url{https://arxiv.org/pdf/2507.02532}

\end{thebibliography}
